### 2010-01-20 docs/architecture/architecture.tex
updates

On a grid, the data can be stored at cell-centers, on a face/edge, or
on the corners.  In boxlib, data that is on an edge is termed `nodal'
in that direction (see figure~\ref{fig:dataloc}.  Data that is on the
corners is nodal in all spatial directions.  In MAESTRO, the state
data (density, enthalpy, velocity, $\ldots$) is generally
cell-centered.  Fluxes are nodal in the direction they represent.
A few quantities are nodal in all directions (e.g.\ $\phi$ used in
the final velocity projection).

\begin{figure}[h]
\centering
\includegraphics[width=6.5in]{\archfigpath/data_loc2}
\caption{\label{fig:dataloc} Some of the different data-centerings:
  (a) cell-centered, (b) nodal in the $x$-direction, and (c) nodal in
  both the $x$- and $y$-directions.  Note that for nodal data, the
  integer index corresponds to the lower boundary in that direction.
  In each of these centerings, the red point has the same indices:\ (1,2).
  Not show is the case where data is nodal in the $y$-direction only.}
\end{figure}

@@

\noindent Here:
\begin{itemize}
\item {\tt dim} is the dimensionality of the data
\item {\tt bx} is a \boxtype\ describing where the data in this
  \fab\ is defined.
\item {\tt pbx} is a \boxtype\ that extends {\tt bx} to include
  any ghostcells
\item {\tt ibx}
\item {\tt nc} is the number of components (how many variables at  
  each grid location).
\item {\tt p} is a pointer to the data, in this case double precision
  ({\tt kind=dp\_t}).  Other \fab\ types exists for other Fortran
  data types.
\end{itemize}

>>>>

On a grid, the data can be stored at cell-centers, on a face/edge, or
on the corners.  In boxlib, data that is on an edge is termed `nodal'
in that direction (see Figure~\ref{fig:dataloc}).  Data that is on the
corners is nodal in all spatial directions.  In MAESTRO, the state
data (density, enthalpy, velocity, $\ldots$) is generally
cell-centered.  Fluxes are nodal in the direction they represent.
A few quantities are nodal in all directions (e.g.\ $\phi$ used in
the final velocity projection).

\begin{figure}[h]
\centering
\includegraphics[width=6.5in]{\archfigpath/data_loc2}
\caption{\label{fig:dataloc} Some of the different data-centerings:
  (a) cell-centered, (b) nodal in the $x$-direction, and (c) nodal in
  both the $x$- and $y$-directions.  Note that for nodal data, the
  integer index corresponds to the lower boundary in that direction.
  In each of these centerings, the red point has the same indices:\ (1,2).
  Not shown is the case where data is nodal in the $y$-direction only.}
\end{figure}

@@

\noindent Here:
\begin{itemize}
\item {\tt dim} is the dimensionality of the data
\item {\tt bx} is a \boxtype\ describing the index space for which this \fab\ is defined
\item {\tt ibx} is a \boxtype\ that describes the index range of the valid data
  for the \fab.  This differes from {\tt bx} when the box is nodal in one more more 
  directions.
\item {\tt pbx} is a \boxtype\ that extends {\tt ibx} to include
  any ghostcells, or equivalently, the physical box for the \fab\
\item {\tt nc} is the number of components (how many variables at  
  each grid location)
\item {\tt p} is a pointer to the data, in this case double precision
  ({\tt kind=dp\_t}).  Other \fab\ types exists for other Fortran
  data types.
\end{itemize}
